Implications of Measurement Errors in Water Use Estimates for Water Management

### 2024-11-13 Codes/1_analysis.qmd
tex version added

results_p <-
  system_data %>%
  dplyr::mutate(results = list(
    run_analysis(
      parameter_sets = par_sets_p, 
      farmer_data, 
      prod_data, 
      num_it = 1000, 
      num_cores = parallel::detectCores() - 2
    )
  )) %>%
  dplyr::select(prod_het, results) %>%
  unnest(cols = c(results)) %>%
  data.table()

@@

```{r}
sum_res <-
  rbind(
    readRDS(here::here("Results/proxy_results_summary.rds")),
    readRDS(here::here("Results/water_results_summary.rds"))
  ) %>%
  .[, dir_cor_txt := paste0("Correlation: ", dir_cor)] %>%
  .[, dir_cor_txt := factor(dir_cor_txt, levels = paste0("Correlation: ", c("-", "0", "+")))] %>%
  .[, prod_het := str_to_title(prod_het)] %>%
  .[, prod_het := factor(prod_het, c("Zero", "Medium", "High"))]
```

>>>>

results_p <-
  system_data %>%
  dplyr::mutate(results = list(
    run_analysis(
      parameter_sets = par_sets_p, 
      farmer_data, 
      prod_data, 
      num_it = 100, 
      num_cores = parallel::detectCores() - 2
    )
  )) %>%
  dplyr::select(prod_het, results) %>%
  unnest(cols = c(results)) %>%
  data.table()

@@

```{r}
sum_res <-
  rbind(
    readRDS(here::here("Results/proxy_results_summary.rds")),
    readRDS(here::here("Results/water_results_summary.rds"))
  ) %>%
  .[, dir_cor_txt := paste0("Correlation: ", dir_cor)] %>%
  .[, dir_cor_txt := factor(dir_cor_txt, levels = paste0("Correlation: ", c("-", "0", "+")))] %>%
  .[, prod_het := str_to_title(prod_het)] %>%
  .[, prod_het := factor(prod_het, c("Zero", "Medium", "High"))]

saveRDS(sum_res, here::here("Results/results_summary.rds"))
```

### 2024-11-13 Codes/2_make_figures.qmd
tex version added

ggsave(here::here("Writing/figures/g_opt_w_dist.pdf"), g_opt_w_dist, height = 5, width = 6)
```

@@

ggsave("Writing/figures/g_profit_quota_w_vs_p.pdf", g_profit_quota_w_vs_p, height = 3.5, width = 6)
```

@@

ggsave("Writing/figures/g_trade_effect_profit.pdf", g_trade_effect_profit, height = 6, width = 6)
```

@@

(
  g_profit_ratio <-
    ggplot(profit_ratio) +
    geom_line(aes(x = ratio, y = prob, color = instrument_type)) +
    facet_grid(u_dev ~ prod_het) +
    xlab("Ratio of Profit under Proxy-based to Water-based systems") +
    ylab("Cumulative Probability") +
    scale_color_discrete(name = "Insturment Type") +
    theme_bw() +
    scale_x_continuous(breaks = x_breaks) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.25)) +
    theme(
      legend.position = "bottom",
      panel.grid.minor = element_blank(),
      panel.spacing.y = unit(0.5, "lines"),
      panel.spacing.x = unit(0.6, "lines")
    )
)
ggsave("Writing/figures/g_profit_ratio.pdf", g_profit_ratio, height = 6, width = 6)
```

@@

ggsave("Writing/figures/g_illustration_homogeneous.pdf", g_illustration_homogeneous, height = 4.5, width = 6.5)
```

@@

ggsave("Writing/figures/g_illustration_homogeneous_with_trade.pdf", g_illustration_homogeneous_with_trade, height = 5, width = 6.5)
```

@@

ggsave("Writing/figures/g_illustration_het.pdf", g_illustration_het, height = 4.5, width = 6.5)
```

>>>>

ggsave(here::here("Writing/figures/g_opt_w_dist.png"), g_opt_w_dist, height = 5, width = 6, dpi = 400)
```

@@

ggsave("Writing/figures/g_profit_quota_w_vs_p.png", g_profit_quota_w_vs_p, height = 3.5, width = 6, dpi = 400)
```

@@

ggsave("Writing/figures/g_trade_effect_profit.png", g_trade_effect_profit, height = 6, width = 6, dpi = 400)
```

@@

(
  g_profit_ratio <-
    ggplot(profit_ratio) +
    geom_line(aes(x = ratio, y = prob, color = instrument_type)) +
    facet_grid(u_dev ~ prod_het) +
    xlab("Ratio of Profit under Proxy-based to Water-based systems") +
    ylab("Cumulative Probability") +
    scale_color_discrete(name = "Insturment Type") +
    theme_bw() +
    scale_x_continuous(breaks = x_breaks) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.25)) +
    theme(
      legend.position = "bottom",
      panel.grid.minor = element_blank(),
      panel.spacing.y = unit(0.5, "lines"),
      panel.spacing.x = unit(0.6, "lines")
    )
)
ggsave("Writing/figures/g_profit_ratio.png", g_profit_ratio, height = 6, width = 6, dpi = 400)
```

@@

ggsave("Writing/figures/g_illustration_homogeneous.png", g_illustration_homogeneous, height = 4.5, width = 6.5, dpi = 400)
```

@@

ggsave("Writing/figures/g_illustration_homogeneous_with_trade.png", g_illustration_homogeneous_with_trade, height = 5, width = 6.5, dpi = 400)
```

@@

ggsave("Writing/figures/g_illustration_het.png", g_illustration_het, height = 4.5, width = 6.5, dpi = 400)
```

### 2024-11-13 Writing/manuscript_typst.qmd
tex version added

---
title: Implications of Measurement Errors in Water Use Estimates for Water Management
author:
  - Taro Mieno^[Department of Agricultural Economics, University of Nebraska Lincoln, tmieno2@unl.edu]
  - Timothy Foster^[Department of WWW, University of Manchester, timothy.foster@manchester.ac.uk]
  - Nicholas Brozovic^[Department of Agricultural Economics, University of Nebraska Lincoln, nbrozovic@nebraska.edu]
abstract: |
  abstract here
acknowledgments: |
  Funding for the research in this manuscript was provided by 
bibliography: DRA.bib
output:
  bookdown::pdf_document2:
    extra_dependencies: ["float"]
    citation_package: natbib
    keep_tex: true
    toc: false
    includes:
      in_header: "preamble.tex"
---

@@

#--- packages ---#
library(data.table)
library(tidyverse)
library(stringr)
library(sf)
library(here)
library(tmap)
library(modelsummary)
library(patchwork)
library(kableExtra)

@@

\newpage

@@

@@

  + shed lights on unintentional consequences of using estiamtes rather than actual measurements

@@

No clear policy design suggestions on how to use water use estiamtes with measurement errors.

@@

Figure \@ref(fig:profit-quota-water-het) below compares profit from agricultural production as a function of actual water use between water and proxy quota across three different production heterogeneity levels and the size of the measurement errors. When there is no heterogeneity in farmers' production function, water quota is the most cost effective way to achieve a water use reduction goal (highest profit achievable for a given level of actual water use). Under this circumstance, proxy quota with unbiased measurement errors achieves worse than water quota due to asymmetry in downside and upside risk of water use. However, as production heterogeneity increases, water quota loses its comparative advantage over proxy quota. It can be shown that water quota always outperforms proxy quota on average irrespective of the degere of production heterogeneity when measurement error is independent and production function is concave (show proof in appendix). Not surprisingly, profit losses of using proxy quota increase as measurement error size increases. Profit loss of using proxy-based quota tends to become greater as the toal realized water use becomes smaller.

```{r profit-quota-water-het, fig.cap = "The impacts of an increase in the degree of measurement error on profit"}
knitr::include_graphics("figures/g_profit_quota_comp_stat.pdf")
```

@@

We now look at simple two-farm examles to build intuition behind the profit loss due to the use of proxy quota in place of water quota. Figure \@ref(fig:illust-homegeneous) presents a case with two homegeneous farmers under water and proxy quota. The red dotted lines indicate the effective water quota. Under the water quota system, both farmers receive 7 inches of water quota. Since the unconstrained profit maximizing water use is `r round(opt_w, digits = 2)` inches, both farmers use up all the allocated quota and use 10 inches of water. Under the proxy quota system, they are allocated the same amount of proxy quota. However, measurement error in proxy quota resulted in effective water quota of 4 and 10 inches for farmer A and B, respectively. Both farmers use their allocated amout of water. Under both proxy and water quota systems, the total water use is 14 inches. Farmer B makes `r pi_dif_2` less under the water quota system compared to the proxy quota system. However, Farmer A makes `r -pi_dif_1` more under the water quota system compared to the proxy quota system. This comes from an important nature of crop production with respsect to water: declining marginal impact of water on crop yield. As can be seen in the profit-water relationship, removing an inch of water from 6 inches has much larger negative impact compared to revmoing an inch of water from 10 inches.

```{r illust-homegeneous, fig.cap = "Illustration of profit loss due to the use of proxy for quota-based regulation: a case of homegeneous producers"}
#| warning: false
knitr::include_graphics("figures/g_illustration_homogeneous.pdf")
```

However, as the heterogeneity of farmers increases, comparative advantage of water quota over proxy quota diminishes. While the performance of both systems declines as the level of heterogeneity increases, water quota is affected more so than the proxy quota system. This is because uniform quota now acts like heterogeneous quota under homogeneous production function because the same quota is given to farmers with heterogeneous water demand. This is illustrated in Figure \@ref(fig:illust-heterogeneous). In this example,  farmer A needs less water than farmer B. Water and proxy quota allocated to the farmers are exactly the same as the previous case. In this example, errors in proxy happened to realize so that more effective water quota is given to farmer B than farmer A. Consequently, proxy quota produces a higher total profit than water quota. Of course, if error happened to go the opposite way, then the performance of proxy quota relative to water quota is even worse compared to the homogeneous case. This is a big contrast to the homogeneous case because water quota is always better than proxy quota in that case. Consequently, proxy quota performs relatively better under heterogeneous cases. On average, the positive and negative effects of measurement errors tend to even out. However, proxy quota is never better than water quota **on average** (see Appendix ... for mathematical proof).

```{r illust-heterogeneous, fig.cap = "Illustration of profit loss due to the use of proxy for quota-based regulation: a case of heterogeneous producers"}
#| warning: false

knitr::include_graphics("figures/g_illustration_het.pdf")
```

@@

Allowing quota to be traded among farmers can dramatically change the relative performance of the water- and quota-based regulation. Figure \@ref(fig:trading-profit) presents profit for water-based quota, proxy-based quota, water-based quota trading, and proxy-based quota trading regulation systems. As shown in the figure, the disadvantage of using proxy almost disappears when trading of quota is allowed. This is because the inefficiencies in quota allocations are resolved through trading of quota whether it is water or proxy quota.

```{r trading-profit, fig.cap = "Comparison of profit from agricultural production between the water and quota systems when quota trading is allowed"}
#| echo: false
knitr::include_graphics("figures/g_trade_effect_profit.pdf")
```

@@

Figure \@ref(fig:trading-profit-illustration) illustrates the impact of allowing for trading proxy quota using the case of two homogeneous farmers illustrated in Figure \@ref(fig:illust-homegeneous). In this illustration, the same water quota of 7 is allocated for both farmers under the water-based systems. No water quota trading would happen as the marginal profit of water is already equated at water use of 7. Under the proxy-base quota system, proxy quota of 7 is allocated for both farmers, but the effective water quota for farmers A and B are 4 and 7, respectively. Once trading of proxy quota is alllowed, farmer A would buy `r farmer_A_purchase` proxy quota from farmer B. At these production levels, the marginal profit of quota (not water) are equated acros the farmers and no further transfer between them would happen. Trading of proxy quota improves the overall profit to `r profit_after_trade_proxy` $/acre from `r profit_before_trade_quota` $/acre.

```{r trading-profit-illustration, fig.cap = "Illustration of the benefits of trading quota"}
#| echo: false
knitr::include_graphics("figures/g_illustration_homogeneous_with_trade.pdf")
```

While water-quota and proxy-quota trading perform about the same, water-quota always leads to a higher total profit for a given level of realized water use. In other words, to achieve a certain water use goal, water-quota trading is always to more cost-effective than proxy-quota trading. Under water-quota trading, the margial profit of water is equalized across the farmers, which is a necessary condition to achieve the highest profit for a given level of total water use. Under proxy-quota trading, the marginal profit of proxy is equalized across the farmers, not the margial profit of water (See Appendix ... for a mathematical proof). However, it is worth emphasizing that the inefficiency caused by the use of proxy is likely to be minimal as shown in Figure \@ref(fig:trading-profit). This point is well-illustrated in Figure \@ref(fig:trading-profit-illustration), where total profit per acre is `r profit_after_trade_water` and `r profit_after_trade_proxy` under the water-quota and proxy-quota trading system, respsectively.

Figure \@ref(fig:trading-profit) presents the simualtion results of proxy-quota and water-quota trading systems added to Figure \@ref(fig:profit-quota-water-het). As you can see at all levels of production heterogeneity levels and the degres of measurement errors, proxy-quota and water-quota trading systems perform almost identical at all levels of realized water use (water-quota trading is always slightly better than proxy-quota trading as explained earlier). Not surprisingly, the benefit of allowing for trading is greater when the degree of measurement errors is larger.

@@

Figure \@ref(fig:distributional-equity) presents the cumulative probability of the ratio of profit under quota-based relative to water-based system for quota (red) and permit trading (blue). Ratio of less than 1 indicates making less profit under the quota-based system compared to the water-based system. If farmers make just as much profir under proxy-based regulation compared to water-based regulation, then the cumulative probability line would be a vertical line at 1. For example, under the high degree of measurement error and medium heterogenenity scenario, some farmers would make about the half of what they would make under the water quota system. At the lower end of the distribution are farmers who would be constrained severely by water quota, but whose water use estiamtes are much higher than their actual water use. At the higher end of the distribution are farmers who would be constrained by water quota, but whose water use estiamtes are much lower than their actual water use. Famres who suffer significantly under the quota system can develop strong dissatisfaction of the quota-based regulation system, which in turn may lead to installing water meter themselves. If they discover the over-estimation of their water use, they may appeal to legal actions against the administrator for their unfair treatment. Allowind quota trading greatly diminishes the distributional inequality, though not completely. This is because unfortunate farmers who suffered from over-estimation of their water use can now at least purchase proxy quota to increase their production level.

```{r distributional-equity, fig.cap = "Distribution of profit under various regulation systems"}
knitr::include_graphics("figures/g_profit_ratio.pdf")
```

@@

Three different sets of the collections of crop-water production functions are generated that vary in the degree of heterogeneity in unconstrained optimal water use ($w^*$). Under no-heterogeneity set, farmers share exactly the same profuction function (the same value of $\phi_i$, $\alpha_i$, and $\beta_i$). Unde the medium-heterogeneity set, model parameters vary and so does $w^*$. Under the high-heterogeneity set, the variance of $w^*$ becomes even greater. The distribution of $w^*$ for each of the sets is presented in Figure \@ref(fig:dist-opt-w).

@@

Three different sets of the distribution of $\eta$ are considered that vary in the degree of heterogeneity in $\eta$: low, medium, and high. For all the sets, $E[\eta] = 1$ (or equivalently $E[\mu] = 0$), meaning that water use estimation is ubiased. A sample of the empirical (realized) distribution of $\eta$ for each of the sets is presented in Figure \@ref(fig:dist-eta).

@@

\clearpage

@@

```{r dist-opt-w, fig.cap = "Distribution of optimal water use under no water use constraints", fig.height = 5}
knitr::include_graphics("figures/g_opt_w_dist.pdf")
```

@@

```{r dist-eta, fig.cap = "Distribution of water-proxy conversion factor", fig.height = 5}
# knitr::include_graphics("figures/g_eta_dist.pdf")
```

\clearpage

>>>>

---
title: "Implications of Measurement Errors in Water Use Estimates for Water Management"
author:
  - name: "Taro Mieno^[University of Nebraska-Lincoln, Email: tmieno2@unl.edu]"
    orcid: 0000-0003-1689-0557
  - name: Timothy Foster^[University of Manchester]
    orcid: 0000-0003-1689-0557
  - name: Nicholas Brozovic^[University of Nebraska-Lincoln]
    orcid: 0000-0003-1689-0557
format:
  pdf:
    toc: false
    keep-tex: true
  html:
    embed-resources: true
  typst:
    toc: false
    keep-typ: true
    section-numbering: 1.1.a
    columns: 1
    fig-format: png
  docx:
    toc: false
bibliography: DRA.bib
bibliographystyle: apa
---

@@

#--- packages ---#
library(here)
library(data.table)
library(dplyr)
library(stringr)

@@

@@

+ Use of satellite imagery in water management in general
  + water theft detection in Australia (Nature Water, Adam Loch)

@@

  + shed lights on unintentional consequences of using estimates rather than actual measurements

@@

No clear policy design suggestions on how to use water use estimates with measurement errors.

@@

@fig-profit-quota-water-het illustrates the profit from agricultural production as a function of actual water use, comparing water quotas and proxy quotas across three levels of production heterogeneity and varying sizes of measurement errors. When there is no production heterogeneity among farmers, the water quota is the most cost-effective mechanism to achieve a targeted reduction in water use (yielding the highest profit for a given level of actual water use). In this scenario, the proxy quota with unbiased measurement errors performs worse than the water quota due to the asymmetry in downside and upside risk of water use. However, as production heterogeneity increases, the comparative advantage of water quotas over proxy quotas diminishes.

It is demonstrated (proof in Appendix) that water quotas consistently outperform proxy quotas on average, regardless of production heterogeneity, when measurement errors are independent and the production function is concave. As expected, the profit losses associated with proxy quotas increase as the size of measurement errors grows. Furthermore, the profit loss from using proxy-based quotas tends to become more pronounced as total realized water use decreases.

```{r}
#| label: fig-profit-quota-water-het
#| fig-cap: "The impacts of an increase in the degree of measurement error on profit"
knitr::include_graphics("figures/g_profit_quota_comp_stat.png")
```

@grafton2018paradox

@@

We now look at simple two-farm examles to build intuition behind the profit loss due to the use of proxy quota in place of water quota. @fig-illust-homegeneous presents a case with two homegeneous farmers under water and proxy quota. The red dotted lines indicate the effective water quota. Under the water quota system, both farmers receive 7 inches of water quota. Since the unconstrained profit maximizing water use is `r round(opt_w, digits = 2)` inches, both farmers use up all the allocated quota and use 10 inches of water. Under the proxy quota system, they are allocated the same amount of proxy quota. However, measurement error in proxy quota resulted in effective water quota of 4 and 10 inches for farmer A and B, respectively. Both farmers use their allocated amout of water. Under both proxy and water quota systems, the total water use is 14 inches. Farmer B makes `r pi_dif_2` less under the water quota system compared to the proxy quota system. However, Farmer A makes `r -pi_dif_1` more under the water quota system compared to the proxy quota system. This comes from an important nature of crop production with respsect to water: declining marginal impact of water on crop yield. As can be seen in the profit-water relationship, removing an inch of water from 6 inches has much larger negative impact compared to revmoing an inch of water from 10 inches.

```{r}
#| label: fig-illust-homegeneous
#| fig-cap: "Illustration of profit loss due to the use of proxy for quota-based regulation: a case of homegeneous producers"
#| warning: false
knitr::include_graphics("figures/g_illustration_homogeneous.png")
```

However, as the heterogeneity of farmers increases, comparative advantage of water quota over proxy quota diminishes. While the performance of both systems declines as the level of heterogeneity increases, water quota is affected more so than the proxy quota system. This is because uniform quota now acts like heterogeneous quota under homogeneous production function because the same quota is given to farmers with heterogeneous water demand. This is illustrated in @fig-illust-heterogeneous. In this example, farmer A needs less water than farmer B. Water and proxy quota allocated to the farmers are exactly the same as the previous case. In this example, errors in proxy happened to realize so that more effective water quota is given to farmer B than farmer A. Consequently, proxy quota produces a higher total profit than water quota. Of course, if error happened to go the opposite way, then the performance of proxy quota relative to water quota is even worse compared to the homogeneous case. This is a big contrast to the homogeneous case because water quota is always better than proxy quota in that case. Consequently, proxy quota can perform relatively better under heterogeneous cases. On average, the positive and negative effects of measurement errors tend to even out. However, proxy quota is never better than water quota **on average** (see Appendix ... for mathematical proof).

```{r}
#| label: fig-illust-heterogeneous
#| fig-cap: "Illustration of profit loss due to the use of proxy for quota-based regulation: a case of heterogeneous producers" 
#| warning: false

knitr::include_graphics("figures/g_illustration_het.png")
```

@@

Allowing quota to be traded among farmers can dramatically change the relative performance of the water- and quota-based regulation. @fig-trading-profit presents profit for water-based quota, proxy-based quota, water-based quota trading, and proxy-based quota trading regulation systems. As shown in the figure, the disadvantage of using proxy almost disappears when trading of quota is allowed. This is because the inefficiencies in quota allocations are resolved through trading of quota whether it is water or proxy quota.

```{r}
#| label: fig-trading-profit
#| fig-cap: "Comparison of profit from agricultural production between the water and quota systems when quota trading is allowed"
#| echo: false
knitr::include_graphics("figures/g_trade_effect_profit.png")
```

@@

@fig-trading-profit-illustration illustrates the impact of allowing for trading proxy quota using the case of two homogeneous farmers illustrated in @fig-illust-homegeneous. In this illustration, the same water quota of 7 is allocated for both farmers under the water-based systems. No water quota trading would happen as the marginal profit of water is already equated at water use of 7. Under the proxy-base quota system, proxy quota of 7 is allocated for both farmers, but the effective water quota for farmers A and B are 4 and 7, respectively. Once trading of proxy quota is alllowed, farmer A would buy `r farmer_A_purchase` proxy quota from farmer B. At these production levels, the marginal profit of quota (not water) are equated acros the farmers and no further transfer between them would happen. Trading of proxy quota improves the overall profit to `r profit_after_trade_proxy` $/acre from `r profit_before_trade_quota` $/acre.

```{r}
#| label: fig-trading-profit-illustration
#| fig-cap: "Illustration of the benefits of trading quota"
#| echo: false
knitr::include_graphics("figures/g_illustration_homogeneous_with_trade.png")
```

While water-quota and proxy-quota trading perform about the same, water-quota always leads to a higher total profit for a given level of realized water use. In other words, to achieve a certain water use goal, water-quota trading is always to more cost-effective than proxy-quota trading. Under water-quota trading, the margial profit of water is equalized across the farmers, which is a necessary condition to achieve the highest profit for a given level of total water use. Under proxy-quota trading, the marginal profit of proxy is equalized across the farmers, not the margial profit of water (See Appendix ... for a mathematical proof). However, it is worth emphasizing that the inefficiency caused by the use of proxy is likely to be minimal as shown in @fig-trading-profit. This point is well-illustrated in @fig-trading-profit-illustration, where total profit per acre is `r profit_after_trade_water` and `r profit_after_trade_proxy` under the water-quota and proxy-quota trading system, respsectively.

@fig-trading-profit presents the simualtion results of proxy-quota and water-quota trading systems added to @fig-profit-quota-water-het. As you can see at all levels of production heterogeneity levels and the degres of measurement errors, proxy-quota and water-quota trading systems perform almost identical at all levels of realized water use (water-quota trading is always slightly better than proxy-quota trading as explained earlier). Not surprisingly, the benefit of allowing for trading is greater when the degree of measurement errors is larger.

@@

@fig-distributional-equity presents the cumulative probability of the ratio of profit under the proxy-based relative to water-based system for quota (red) and permit trading (blue). Ratio of less than 1 indicates making less profit under the proxy-based system compared to the water-based system. If farmers make just as much profit under proxy-based regulation compared to water-based regulation, then the cumulative probability line would be a vertical line at 1. For example, under the high degree of measurement error and medium heterogenenity scenario, some farmers would make about the half of what they would make under the water quota system. At the lower end of the distribution are farmers who would be constrained severely by water quota, but whose water use estiamtes are much higher than their actual water use. At the higher end of the distribution are farmers who would be constrained by water quota, but whose water use estiamtes are much lower than their actual water use. Famres who suffer significantly under the quota system can develop strong dissatisfaction of the quota-based regulation system, which in turn may lead to installing water meter themselves. If they discover the over-estimation of their water use, they may appeal to legal actions against the administrator for their unfair treatment. Allowind quota trading greatly diminishes the distributional inequality, though not completely. This is because unfortunate farmers who suffered from over-estimation of their water use can now at least purchase proxy quota to increase their production level.

```{r}
#| label: fig-distributional-equity 
#| fig-cap: "Distribution of profit under various regulation systems"
knitr::include_graphics("figures/g_profit_ratio.png")
```

@@

Three different sets of the collections of crop-water production functions are generated that vary in the degree of heterogeneity in unconstrained optimal water use ($w^*$). Under no-heterogeneity set, farmers share exactly the same profuction function (the same value of $\phi_i$, $\alpha_i$, and $\beta_i$). Unde the medium-heterogeneity set, model parameters vary and so does $w^*$. Under the high-heterogeneity set, the variance of $w^*$ becomes even greater. The distribution of $w^*$ for each of the sets is presented in @fig-dist-opt-w.

@@

Three different sets of the distribution of $\eta$ are considered that vary in the degree of heterogeneity in $\eta$: low, medium, and high. For all the sets, $E[\eta] = 1$ (or equivalently $E[\mu] = 0$), meaning that water use estimation is ubiased. A sample of the empirical (realized) distribution of $\eta$ for each of the sets is presented in @fig-dist-eta.

@@

@@

```{r}
#| label: fig-dist-opt-w
#| fig-cap: "Distribution of optimal water use under no water use constraints"
knitr::include_graphics("figures/g_opt_w_dist.png")
```

@@

```{r}
#| label: fig-dist-eta
#| fig-cap: "Distribution of water-proxy conversion factor" 
# knitr::include_graphics("figures/g_eta_dist.png")
```
